### 2019-03-11 papers/journal/synth-dia.tex
use subcaption to put fig along side

\begin{figure}[t]
	\centering
	%\begin{minipage}{0.45\linewidth

\begin{tikzpicture}[->,>=stealth',auto,node distance=4cm,
  thick,main node/.style={rectangle,draw}]
  	\begin{scope}[]
  \node[main node] (pm) {PM { \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
  \node[main node] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
  \node[main node] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};

  %le <-> pm
  \path (le) edge[bend right=30] node [above] {Qb7 Qc7} (pm);
  %ee -> le
  \path (ee) edge[bend right] node [below,rotate=70] {\^{R8},Qa7, Qbc7,R7} (le);

  %pm <-> ee
  \path (ee) edge[bend left=30] node [above] {\^{R3}} (pm);
  \path (pm) edge[bend left=30] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  \end{scope}

  \begin{scope}[xshift=2cm,yshift=-1.0cm]
  \node[main node,text width=2.0cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2 ... } \^{Qbc7}}};
  \node[main node, text width=2.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
  \node[main node] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8} ...}};

@@

  %pm <-> ee
  \path (ee) edge[bend left=30] node [above] {\^{R3, {\color{blue} { \textbf{\^{Qa2,}, \^{Qa7}, \^{R2}}}}}} (pm);
  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);

  \end{scope}
 \end{tikzpicture}
  \caption{An example of synthesis of edge and molecules in partial VTS.} \label{fig:synth-vts}
\end{figure}

>>>>

\begin{figure}[t]
%	\centering
	%\begin{minipage}{0.45\linewidth
 \begin{subfigure}[b]{0.49\linewidth}

	\begin{tikzpicture}[->,>=stealth', auto , node distance=3.0cm,
	  thick,main node/.style={rectangle,draw}]
	 % 	\begin{scope}[]
	  \node[main node, text width=1.5cm] (pm) {PM { \^{Qa5} 
	  		                     \^{Qa7} \^{Qbc2} \^{Qbc7}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE { \^{Qa2} \^{Qb2/3} \^{Qc2/3}}};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE { \^{Qa8} \^{Qb8} \^{Qc8}}};

	  %le <-> pm
	  \path (le) edge[bend right=30] node [above] {Qb7 Qc7} (pm);
	  %ee -> le
	  \path (ee) edge[bend right, text width=3.0cm] node [below,rotate=65] {\^{R8},Qa7, Qbc7,R7} (le);

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [above] {\^{R3}} (pm);
	  \path (pm) edge[bend left=30, text width=2.5cm] node [above,rotate=-45] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);
	\end{tikzpicture}
  \end{subfigure}%
 % \end{scope}
%  \vspace{1.2cm}
  \begin{subfigure}[b]{0.49\linewidth}
	  \begin{tikzpicture}[->,>=stealth',auto,node distance=3.0cm,
	  thick,main node/.style={rectangle,draw}]
	 % \begin{scope}[xshift=3.5cm,yshift=0.0cm]
	  \node[main node,text width=1.5cm] (pm) {PM {\small \^{Qa5} \^{Qa7} \^{Qbc2} \^{Qbc7}}};
	  \node[main node, text width=1.5cm] (ee) [below right of=pm] {EE {\small \^{Qa2} \^{Qb2/3} \^{Qc2/3} ... }};
	  \node[main node, text width=1.5cm] (le) [above of=ee,yshift=-10mm,xshift=23mm] {LE {\small \^{Qa8} \^{Qb8} \^{Qc8}}};

@@

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [above] {\^{R3, {\color{blue} { \textbf{\^{Qa2,}, \^{Qa7}, \^{R2}}}}}} (pm);
	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {\^{R2} {Qa7} Qbc7, R7, Qc7, Qa2} (ee);	    
	 % \end{scope}
	 \end{tikzpicture}
  \end{subfigure}%
  \caption{An example of synthesis of edge and molecules in partial VTS.} \label{fig:synth-vts}
\end{figure}
